### 2022-06-01 main/chapter_2ljets.tex
add disco plots

\subsection{High}
\label{sec:2ljets_high}

Table~\ref{tab:2ljets_high}.

@@

\subsection{Intermediate}
\label{sec:2ljets_int}

Table~\ref{tab:2ljets_int}.

@@

\TODO{}
\begin{verbatim}
2ljets_disco_High_C1N2_WZ_500p0_200p0_2L2J.png
2ljets_disco_High_C1N2_WZ_600_0_2L2J.png
2ljets_disco_Int_C1N2_WZ_250p0_100p0_2L2J.png
2ljets_disco_Int_C1N2_WZ_400p0_200p0_2L2J.png
2ljets_disco_llbb_C1N2N1_GGMHinoZh50_700.png
\end{verbatim}

>>>>

\subsection{High}
\label{sec:2ljets_high}
Table~\ref{tab:2ljets_high}.

@@

\subsection{Intermediate}
\label{sec:2ljets_int}
Table~\ref{tab:2ljets_int}.

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_High_C1N2_WZ_500p0_200p0_2L2J.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_High_C1N2_WZ_600_0_2L2J.png}
\caption{}
\end{subfigure}
\caption{%
Evaluation of candidate High discovery regions.
The region SR-High-8, labelled `High8\_1+\_2' here, is chosen for its
simplicity and good sensitivity to both benchmark signal models.
Upper plots show background and signal yields.
Lower plots show various measures of projected
sensitivity~\cite{cousins2008evaluation}.
Yields are derived in an early iteration of the analysis and do not exactly
match those in the final result.
}
\label{fig:2ljets_disco_trials_high}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_600.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_700.png}
\caption{}
\end{subfigure}
\\[.5em]
\caption{%
Evaluation of candidate High discovery regions.
The region SR-$\ell\ell bb$, labelled `SRllbb' here, is chosen for
sensitivity, simplicity, and to avoid overlapping with DR-High.
Upper plots show background and signal yields.
Lower plots show various measures of projected
sensitivity~\cite{cousins2008evaluation}.
Yields are derived in an early iteration of the analysis and do not exactly
match those in the final result.
}
\label{fig:2ljets_disco_trials_llbb}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_Int_C1N2_WZ_250p0_100p0_2L2J.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_Int_C1N2_WZ_400p0_200p0_2L2J.png}
\caption{}
\end{subfigure}
\caption{%
Evaluation of candidate High discovery regions.
The region SR-Int, labelled `Int\_1+\_2' here, is chosen for its simplicity
and broad sensitivity.
Upper plots show background and signal yields.
Lower plots show various measures of projected
sensitivity~\cite{cousins2008evaluation}.
Yields are derived in an early iteration of the analysis and do not exactly
match those in the final result.
}
\label{fig:2ljets_disco_trials_int}
\end{figure}
